Assessing \Htwo{} and \COtwo{} Network Strategies in Europe

### 2023-12-11 report/submissions/journal/paper/paper.tex
maps: re-add sequestration to legend

\begin{figure*}[ht!]
    \centering
    \includegraphics[width=\linewidth]{comparison/single-technologies/figures/90_nodes/balance_map_dedicated.png}
    \caption{Optimal operation, flows and prices of the carbon (top line) and hydrogen (bottom line) sectors for the \carbonmodel{} (left) and the \hydrogenmodel{} (right) in the net zero scenario. For each region, upper semicircles show the average production per technology, lower semicircles the consumption, and colors the average marginal prices. Lines and arrows show the interregional transportation. Both models transport \carbon{} and \hydrogen{} respectively from areas with low prices to areas with high prices to supply CU and, in the case of \carbonmodel{}, CS.
    }
    \label{fig:balance_map}
\end{figure*}

@@

\begin{figure*}[ht!]
    \centering
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{full/figures/90_nodes/balance_map_carbon.png}
        \label{fig:capacity_map_carbon_co2}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{full/figures/90_nodes/balance_map_hydrogen.png}
        \label{fig:capacity_map_hydrogen_co2}
    \end{subfigure}
    \caption{Optimal operation, flows and prices of the carbon (left) and hydrogen (right) sectors for the \hybridmodel{} in the net zero scenario. For each region, upper semicircles show the average production per technology, lower semicircles the consumption, and colors the average marginal prices. Lines and arrows show the interregional transportation. \carbon{} from point-source in the inland either supplies local CU with imported \hydrogen{} or facilitates sequestration in nearby offshore regions.
    % Carbon network looks the same as in~\cite{morbeeOptimisedDeploymentEuropean2012}: two backbones, one in the nothern Europe other in south east.
    }
    \label{fig:capacity_maps}
\end{figure*}

>>>>

\begin{figure*}[ht!]
    \centering
    \includegraphics[width=\linewidth]{comparison/single-technologies/figures/90_nodes/balance_map_dedicated.png}
    \caption{Optimal operation, flows and prices of the carbon (top line) and hydrogen (bottom line) sectors for the \carbonmodel{} (left) and the \hydrogenmodel{} (right) in the net zero scenario. For each region, upper semicircles show the average production per technology, lower semicircles the consumption, and colors the average marginal prices. Lines and arrows show the interregional transportation. Carbon sequestration offshore are drawn as full circles. \carbon{} and \hydrogen{} transport goes from low price to high price areas to supply CU and, in the case of \carbonmodel{}, CS.
    }
    \label{fig:balance_map}
\end{figure*}

@@

\begin{figure*}[ht!]
    \centering
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{full/figures/90_nodes/balance_map_carbon.png}
        \label{fig:capacity_map_carbon_co2}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{full/figures/90_nodes/balance_map_hydrogen.png}
        \label{fig:capacity_map_hydrogen_co2}
    \end{subfigure}
    \caption{Optimal operation, flows and prices of the carbon (left) and hydrogen (right) sectors for the \hybridmodel{} in the net zero scenario. For each region, upper semicircles show the average production per technology, lower semicircles the consumption, and colors the average marginal prices. Carbon Sequestration offshore are drawn as full circles. Lines and arrows show the interregional transportation. \carbon{} from point-source in the inland either supplies local CU with imported \hydrogen{} or facilitates sequestration in nearby offshore regions.
    % Carbon network looks the same as in~\cite{morbeeOptimisedDeploymentEuropean2012}: two backbones, one in the nothern Europe other in south east.
    }
    \label{fig:capacity_maps}
\end{figure*}
